INTELLIGENT SYSTEMS

### 2021-04-11 paper_6.tex
finish 6.4.5

\subsubsection{Qualitative Results}

>>>>

\subsubsection{Qualitative Results}
Another purpose of the model was to carry out a semantic segmentation also on the different objects, belonging to different categories, present in a single image, in order to be able to distinguish them. A small example of multiple segmentation on different objects is shown in figure \ref{fig:segmentationCategories}.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper6/multiple segmentation.png}
    \centering
    \caption{Example of semantic segmentation on different categories.}
    \label{fig:segmentationCategories}
\end{figure}

\subsubsection{Foreground Segmentations Results}
